\documentclass[../01_main.tex]{subfiles}

\begin{document}

\section*{Abstract}

The electrocardiograms (ECG) is the most common diagnostic tool used for heart 
diseases. Because heart diseases claim more lives each year than any other 
disease, proper analysis of ECGs is very important. For humans, learning how to
read an ECG is very difficult and even with a lot of training, mistakes are
common. One proposed to solution to this problem is computerized ECG analysis
which aims to use the power of computers to improve and speed up the analysis 
of ECGs and to save lives. But even computers have their limits, and working 
with large ECG recordings can take a prohibitively long time. One approach to
speeding up the analysis process is to transform the ECG into a more compact
form--a representation. These representations can be used to more efficiently
store and compare two ECGs. The Symbolic Aggregate Approximation (SAX) is a 
prominent such representation method that has been modified to properly 
represent time series that record more than one value for each moment in time,
e.g. ECGs. This modification is known as Multivariate SAX (MSAX). 
Besides representing
ECGs, SAX can also be used as part of an algorithm called HOT SAX, that can 
find discords in ECGs. ECG discords are segments of the ECG that are very
different from the other segments. Because they are so different, they are
likely to be indicators of disease and thus their discovery can help
a cardiologist save lives.\par

This research compares the use of MSAX with the HOT SAX algorithm (HOT MSAX) to
the use of standard HOT SAX. The novel contributions of this research are to
use MSAX as the representation for HOT SAX, and the application of MSAX to ECG
discord discovery. Because MSAX is meant to represent time series like ECGs and
SAX is not, the recall value for HOT MSAX-based ECG discord discovery should be
greater than the recall value for the HOT SAX-based method. Through
experimental testing using the MIT-BIH Arrhythmia Database it is shown that,
when each method is used with its optimal parameters, there is no significant
difference between HOT SAX and HOT MSAX. Nonetheless, HOT MSAX performs as well
as HOT SAX and could thus find applications in ECG discord discovery by
pre-selecting potentially relevant ECG segment for the cardiologist to
analyze and thus speeding up and simplifying the diagnosis process.

\par
\medskip
\noindent
\textbf{Keywords}: \thesiskeywords{}
\TODO{put more methods into the keywords}

\end{document}
