\documentclass[../01_main.tex]{subfiles}

\begin{document}

\subsection{Discussion}

This section discussed the results presented in the previous section. It was
found that both HOT SAX and HOT MSAX perform poorly when the subsequence length
parameter is not equal to the PAA segment count parameter. A possible cause of
this is the way annotations were counted as True Positives and True Negatives
(covered in section \TODO{refer to this section of the text}). By only counting
the annotations in the segment they fall into, a possible influence of the
discord on the following segments is neglected. This could lead to HOT SAX and
HOT MSAX identifying a discord caused by an abnormal hearbeat in the segment
following the annotation and thus lead to the detection being labeled
a False Positive. By making the subsequences as large as possible, the chance
of this happening become smaller and accordingly, the recall value would
increase. By setting the parameter $m$ equal to $w$ in the second dataset, the
number and proportion of parameter sets satisfying the 95\% recall condition
increased.\par

Every set of parameters in the top 10 values of S-SAX, D-SAX, and MSAX had its
$k=-1$. The parameter $k$ controls how many of the discords identified by HOT
SAX and HOT MSAX will be returned after the computation is finished. Parameter
$k$ being equal to -1 for the optimal parameters regardless of the method
indicates that the highest concrete values of $k$, 300 for dataset 2, is too
low to enable top recall values. This behavior may be explained by considering
the precision values. If the average precision of HOT SAX and HOT MSAX is 
$\approx$ 36\% and the goal is to maximize recall, restricting the number of 
detected discords that are used will directly lower the recall value.\par

Comparing S-SAX, D-SAX, and MSAX showed that MSAX performs acceptably for 5.1\%
of all parameter combinations in dataset 2. S-SAX performed accpetably for
1.2\% and D-SAX for 3.9\%. From this is it inferred that MSAX is more robust
when it comes to parameter choice. All three methods were tested with the same
parameters, but MSAX performed acceptably for a larger share than the other
methods. This is relevant because in applications involving unknown data, the
parameter selection cannot be optimized without testing. A more robust method
could still perform adequately in such a situation.\par

The optimal parameter sets for the three methods all had a value of $k=-1$,
which may be the result of the subsegment-annotation relationship mentioned
above. The PAA segment values and thus the subsequence lengths for D-SAX and
MSAX were 12 compared to 36 for S-SAX. The dimension reduction ratio for MSAX
and D-SAX is 30, while it is 10 for S-SAX. A possible explanation for this is
that MSAX and D-SAX are better suited to the multivariate discord detection 
tasks tested here. As a result of that, they do not require as much 
information as the
less-effective S-SAX method to achieve the same recall values. The information
requirement is relevant because, while PAA, SAX, and MSAX all lower-bound the
Euclidean Distance and thus accurately represent the raw time series, each
average trades a decrease in information about the shape of the time series for
a reduced dimension. If S-SAX is less effective at extracting information from
a multivariate time series, higher numbers of PAA segments may be required to
gain enough information to achieve high recall values.\par

The interquartile ranges of the recall value for all three optimal methods are not
significantly different. The median recall value is very similar across
all three methods as well. The number of outliers is 11 for S-SAX and 6 for the
other two methods. The larger number of outliers for the S-SAX method could be
attributed to it not considering the multivariate nature of ECGs. All observed
outliers were outliers below the median recall value, indicating that certain
ECGs are more difficult for the method to analyze than others. This is
especially true for S-SAX, which does not properly take the nature of ECGs into
account. This result should not be surprising, as both D-SAX and MSAX use all
the information available, while S-SAX does not and is thus put at
a disadvantage.

A correlation between the optimal S-SAX, D-SAX, or MSAX methods and the recall 
value 
has not been found. As a result, the hypothesis of this paper cannot be
supported. There is no evidence of HOT MSAX improving the recall value compared
to HOT SAX. \textcite{anacleto2020}, in the paper introducing MSAX, analyzed
a different ECG dataset as part of a collection of different time series. They
used a $k$-Nearest-Neighbor classifier and found that there is no significant
difference between the SAX representation and the MSAX representation when
applied to ECG analysis. Their findings support this research's results.

\end{document}

showed parameter
sets with $k=-1$. The best parameter sets under these conditions had values of
$w$ that were $\le 12$. Only the 7th to 10th best parameter combinations had $w
\ge 12$. \TODO{make a table here}\TODO{do this for single and dual SAX}. As
these values are average values, they have to investigated more closely with
regards to their outliers and interquartile range. The following boxplot can
illustrate the recall and precision rates for these parameter combinations.

\TODO{boxplots of each of the result sections}
\TODO{top 10 table for each of the methods}
\TODO{investigate correlation between sax and msax for those and see if it is
significant}

\section{Discussion}

\TODO{expand on this, potentially merge with results section}

In the previous section the results of the data analysis were presented. It was
found that when the optimal parameters for MSAX and dual SAX are used, there is
no significant difference between the two methods. This shows, that for optimal
parameter settings, the MSAX representation is equal in performance to the 
dual SAX method when applied to ECGs using HOT SAX. This is congruent with 
the results of \mycite{anacleto2020}, where the authors found only a slight 
difference between the dual SAX method and MSAX. Discussing the actual 
parameters, MSAX used a PAA segment count of 6, representing 60 times reduction 
in dimension, while dual SAX performed best for $w=12$, a 30 times reduction in 
dimension.

\end{document}

\TODO{what do your results mean?
\\- make sure to distiguish results and interpretation "I infer that"...
\\- start with summary of important results
\\- major patterns
\\- relations, trends, generalizations
\\- exceptions
\\- likely causes for the things above?
\\- agreement / disagreement with previous work
\\- interpret with respect to hypothesis
\\- hypothesis testing here?
\\- other questions this relates to?
\\- consider all possibilities
\\- what new insight have we gained?
\\- include the supporting evidence for each line of reasoning
\\- what is the significance of the current results
\\- cite related results
}

\subsection{MSAX vs SAX}

\TODO{use the results from the previous section to come to a conclusion}

\begin{itemize}
    \item do proper hypothesis testing of my hypothesis statement
    \item argue which sets of parameters are the most effective
    \item judge if I proved what I set out to prove
    \item what are the uses of this method
    \item which applications could this fit?
    \item what should be done in future research
\end{itemize}

\end{document}
