\documentclass[../01_main.tex]{subfiles}

\begin{document}

\section{Conclusion}

This work has investigated the use of the MSAX time series representation for 
ECG discord discovery. This novel contribution is based on using the HOT SAX 
algorithm with the MSAX representation, a process called HOT MSAX in this
research. The MIT-BIH ECG database was used to evaluate the HOT SAX and HOT
MSAX algorithms experimentally. Each algorithm's parameters were optimized
based on the results of the evaluation. The recall value for HOT MSAX was 
compared to the recall value for HOT SAX when both are using optimal
parameters. A correlation test was performed to determine if HOT MSAX increases 
the recall value compared to HOT SAX. No correlation was found between the
methods used with optimal parameters and the resulting recall. Accordingly, 
this work's 
hypothesis cannot be supported because HOT MSAX did not significantly improve 
discord discovery recall compared to HOT SAX.\par

The application of the MSAX representation to ECG analysis is novel and follows
the future applications mentioned in \mycite{anacleto2020}. A further
contribution to the literature is the application of the HOT SAX algorithm to 
the MSAX representation. This expands the use of HOT SAX to multivariate time
series in the form of HOT MSAX. In possible future research, HOT MSAX can be
applied to different and unknown datasets to test the optimality of the
parameters determined in this work and judge its performance in discovering
different types of ECG discords, for example those caused by ischaemic heart
disease.

\end{document}

